---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# amstools

Amstools is a (mostly) NOSAMS specific package for working with AMS data and
the NOSAMS database. The goal of amstools is to provide functions for common
AMS data tasks, like getting data for a wheel, sample type, or any group of
samples from the database. It provides functions for converting AMS data among
common formats, and useful bits like how many samples and wheels were run in
a given period. 

## Installation

You can install amstools from github with:

```{r gh-installation, eval = FALSE}
install.packages("devtools")
devtools::install_github("blongworth/amstools")
```

To interact with the NOSAMS DB, you'll need the odbc package installed and
a working connection to the NOSAMS database via ODBC. An ODBC connection string
should be stored in an environment variable called CONSTRING. The package has
been tested with the Microsoft MSSQL driver on Windows and Mac OS X, and with
the unixODBC and FreeTDS drivers on Linux.

If a Data Source Name (DSN) is set up within your odbc system, a CONSTRING
variable in the following format will work:

```
"DSN=database;UID=username;PWD=password"
```

This can be done from R with the `Sys.setenv` command, but this may or may not
be persistent depending on your environment.
