---
title: "Using amstools"
author: "Brett Longworth"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using amstools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The amstools is a (mostly) NOSAMS specific package for working with AMS data and the NOSAMS database.

## Installing

The package should be installed from github. You'll need the `devtools` package installed.

```{r, eval=FALSE}
devtools::install_github("blongworth/amstools")
```

To interact with the NOSAMS DB, you'll need a working ODBC driver and connection for the database. The easiest way to check this is with the Rstudio Connections tab. Amstools looks for your database credentials in an environment variable called CONSTRING, which should be in the following format:


```
"DSN=database;UID=username;PWD=password"
```

The database also has to be set up as an ODBC connection.

## Getting started

First, load the library.

```{r}
library(clivartools)
```

A list of functions in the package should help you get started. Most functions are tersely documented, but the functions are commented.

## Some useful functions

