---
params:
  rec: 177225
title: "Data for rec_num `r sprintf('%i', params$rec)`"
author: "BEL"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r echo=FALSE, message=FALSE}
#Load Libraries
library(amstools)
library(amsdata)
library(ggplot2)
library(dplyr)
library(knitr)
library(odbc)

options(digits = 4)

#set parameters- from, to, sys not used if loading from file
from <- '2014-09-01'
to <- 'present' #present or date
sys <- 'both' #cfams, usams, ams1 or both

#Pull the data
ss <- getRecSR(recnum = params$rec)

# get sample name
db <- conNOSAMS()
name <- dbGetQuery(db, paste("select cl_id from logged_sample where rec_num =", params$rec))
```

Determination of mean fm and error for `r name`, rec num `r sprintf('%i', params$rec)`.

Data pulled from snics_results by rec_num.
Here's the data...

```{r, echo=FALSE, message=FALSE}
ggplot(ss, aes(fm_corr)) + geom_histogram()
ggplot(ss, aes(dc13)) + geom_histogram()

kable(select(ss, tp_num, tp_date_pressed, wheel, fm_corr, sig_fm_corr, dc13))
```

And the weighted mean and SD.

```{r}
# means
fmmean <- mean(ss$fm_corr)
fmsd <- sd(ss$fm_corr)
```

That leaves us with N = `r nrow(ss)`, mean = `r mean(ss$fm_corr)`, weighted mean = `r weighted.mean(ss$fm_corr, ss$sig_fm_corr)`, sd = `r sd(ss$fm_corr)`. Mean d13C = `r mean(ss$dc13, na.rm=TRUE)`, sd = `r sd(ss$dc13, na.rm=TRUE)`.


Remove clear outliers. Discard points > 3 * SD.

```{r}
ssnol <- ss %>% 
  filter(fm_corr > fmmean - fmsd,
         fm_corr < fmmean + fmsd)
  
```


```{r, echo=FALSE, message=FALSE}
ggplot(ssnol, aes(fm_corr)) + geom_histogram()
ggplot(ssnol, aes(dc13)) + geom_histogram()
```

And the weighted mean and SD without outliers.

That leaves us with N = `r nrow(ssnol)`, mean = `r mean(ssnol$fm_corr)`, weighted mean = `r weighted.mean(ssnol$fm_corr, ssnol$sig_fm_corr)`, sd = `r sd(ssnol$fm_corr)`. Mean d13C = `r mean(ssnol$dc13, na.rm=TRUE)`, sd = `r sd(ssnol$dc13, na.rm=TRUE)`.
